Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-17 WSSSPE2_report/WSSSPE2_review.tex
Section 2: Change list margin.
Section 2: line breaks.

@@

\begin{quote}
We invite short (4-page) \textbf{actionable} papers that will lead to improvements for sustainable software science. These papers could be a call to action, or could provide position or experience reports on sustainable software activities. The papers will be used by the organizing committee to design sessions that will be highly interactive and targeted towards facilitating action. Submitted papers should be archived by a third-party service that provides DOIs. We encourage submitters to license their papers under a Creative Commons license that encourages sharing and remixing, as we will combine ideas (with attribution) into the outcomes of the workshop.\end{quote}

@@

The review process was fairly standard, where reviewers bid for papers, then an automated system
matched bids to determine assignments, and reviewers then completed their assigned
reviews (with an average of 4.9 reviews per paper, and 4.1 reviews per reviewer)
This process was done through EasyChair\footnote{http://easychair.org/}, which allowed reviewers to provide scores on relevance and comments to the organizers, which were used to decide which papers to associate with the workshop, and comments to the authors, which were provided back to the authors to allow them to improve their papers.

>>>>

\usepackage{enumitem}
\setlist{leftmargin=3mm}

@@

\begin{quote}
We invite short (4-page) \textbf{actionable} papers that will lead to
improvements for sustainable software science. These papers could be a call to
action, or could provide position or experience reports on sustainable software
activities. The papers will be used by the organizing committee to design
sessions that will be highly interactive and targeted towards facilitating
action. Submitted papers should be archived by a third-party service that
provides DOIs. We encourage submitters to license their papers under a Creative
Commons license that encourages sharing and remixing, as we will combine ideas
(with attribution) into the outcomes of the workshop.
\end{quote}

@@

The review process was fairly standard, where reviewers bid for papers, then an
automated system
matched bids to determine assignments, and reviewers then completed their
assigned
reviews (with an average of 4.9 reviews per paper, and 4.1 reviews per
reviewer).
This process was done through EasyChair\footnote{http://easychair.org/}, which
allowed reviewers to provide scores on relevance and comments to the organizers,
which were used to decide which papers to associate with the workshop, and
comments to the authors, which were provided back to the authors to allow them
to improve their papers.
